### 2011-10-28 Text/paper.tex
Started analyzing small results available.

>>>>

\subsection{Comparison between different boundary conditions}
The mass transfer coefficient by the definition of used in the paper of \citet{vanbaten} is as
follows:

In what follows we will examine different boundary conditions for the mass transfer:
\begin{description}
 \item[I] Placement the bubble near the entrance with the periodic bondary conditions and using the
outlet concentration as the characteristic value of the 
\item[II] 
\end{description}

\begin{figure}[htb!]
\caption{Comparison between different simulations and definitions of the characteristic
concentration.}
\end{figure}
